Optimizing Large Scale Surveys for Photometric Calibration, \\ The Euclid Dark Energy Mission as an Example

### 2011-07-03 Documentation/cross_cal_paper.tex
euclid: paper update, plotting function update: nicer figures
git-svn-id: svn+ssh://astrometry.net/svn/trunk/projects/euclid@18944 03a3cea6-2c03-0410-ac9b-9271b1c66c29

>>>>

The difference between the performance of the cross-calibration between Surveys A and B and Surveys C and D is striking. With the former, the solution does not converge. With the later, a fit to the relative instrument response is found after a small number of iterations XX. In both cases, the cross-calibration procedure is able to reproduce the actual instrument response to a high accuracy, with Survey D performing slightly better.
